Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-26 sections/eval.tex
Update on Overleaf.

Figure~\cite{graph_result} (a) \changwan{add (a) in fig} shows BFS speedup over Graphs.jl, a BFS implementation with push traversal of Julia. `finch\_push\_only` only uses push traversal, whereas `finch\_push\_pull` applies direction-optimization used in GraphBLAS. Finch supports push/pull traversal, early break, so it supports direction-optimization. Finch also supports As shown in Figure~\cite{graph_result} (a), direction-optimization significantly improves the performance for scale-free graphs. \changwan{how much average speedup?}

>>>>

Figure~\cite{graph_result} (a) \changwan{add (a) in fig} shows BFS speedup over Graphs.jl, a BFS implementation with push traversal of Julia. `finch\_push\_only` only uses push traversal, whereas `finch\_push\_pull` applies direction-optimization used in GraphBLAS. Finch supports push/pull traversal, early break, so it supports direction-optimization. Finch also supports the different loop orders and multiple outputs, which also As shown in Figure~\cite{graph_result} (a), direction-optimization significantly improves the performance for scale-free graphs. \changwan{how much average speedup?}
